Summary Tables

### 2022-10-23 summary_tables.Rmd
updated input file and corrected ouput file path

# Export ylls HB
write.csv(ylls,
            "results/multi_city/health_impacts/ylls.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            "results/multi_city/health_impacts/ylls_pathway.csv",
            row.names = F)
# Export deaths HB
write.csv(deaths,
            "results/multi_city/health_impacts/deaths.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            "results/multi_city/health_impacts/deaths_pathway",
            row.names = F)

>>>>

# Export ylls HB
write.csv(ylls,
            "results/multi_city/health_impacts/ylls.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            "results/multi_city/health_impacts/ylls_pathway.csv",
            row.names = F)
# Export deaths HB
write.csv(deaths,
            "results/multi_city/health_impacts/deaths.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            "results/multi_city/health_impacts/deaths_pathway.csv",
            row.names = F)
